### 2019-05-06 papers/haskell19/2-sources.tex
Nit

\begin{code}
simplify :: Html -> Html
simplify (Text t1 iJoin Text t2) = Text (t1 ++ t2)
simplify ((Text t1 iJoin x) iJoin y)
  = simplify (Text t1 iJoin simplify (x iJoin y))
simplify (x iJoin y) = simplify x iJoin simplify y
simplify (Tag t x) = Tag t (simplify x)
simplify x = x
\end{code}
%
This function simply traverses |Html| values, joining together every contiguous
pair of |Text| constructors.
%
Ideally, we would like to put approximately the same testing effort info each
clause of |simplify|, or perhaps even more to the first two ones, since those
are the ones performing actual simplifications.
%
However, these two clauses are the most difficult ones to test in practice!
%
The probability of generating a random value satisfying nested patterns
decreases multiplicatively with the number of constructors we simultaneously
pattern match against to.

>>>>

\begin{code}
simplify :: Html -> Html
simplify (Join (Text t1) (Text t2)) = Text (t1 ++ t2)
simplify (Join (Join (Text t) x) y)
  = simplify (Text t1 iJoin simplify (x iJoin y))
simplify (Join x y) = simplify x iJoin simplify y
simplify (Tag t x) = Tag t (simplify x)
simplify x = x
\end{code}
%
This function simply traverses |Html| values, joining together every contiguous
pair of |Text| constructors.
%
Ideally, we would like to put approximately the same testing effort info each
clause of |simplify|, or perhaps even more to the first two ones, since those
are the ones performing actual simplifications.
%
However, these two clauses are the most difficult ones to test in practice!
%
The probability of generating a random value satisfying nested patterns
decreases multiplicatively with the number of constructors we simultaneously
pattern match against to.
